My title

### 2024-02-11 paper/paper.qmd
change

```{r}
#| include: false
#| warning: false
#| message: false
install.packages("haven")  # Install the haven package
library(haven)  # Load the haven package
library(tidyverse)
library(palmerpenguins)
library(dplyr)
```

@@

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}
@fig-country
```{r fig.height=8, fig.width=10 }
#| label: fig-country
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

data <-  read.csv(file = here::here("outputs/data/clean_country_data.csv"))

data <- data[order(-data$prison_population_rate), ]

# Create the bar plot
plot <- ggplot(data, aes(x =prison_population_rate, y = country)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1, vjust = 0.5)) +  # Rotate x-axis labels
  labs(x = "Prison Population Rate", y = "country") +  # Add axis labels
  ggtitle("Prison Population Rate by Country ")  # Add title

print(plot)

Some of our data is of penguins (@fig-bill), from @palmerpenguins.
```{r fig.height=8, fig.width=10 }
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

@@

```{r }
#| label: fig-plane
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

data_1 <- read_dta('../../inputs/data/spi86to16.dta')

x <- data_1[data_1$admit==0,]

drugev  <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(drugev, wt, na.rm=T)))
drugev  <- drugev[!is.nan(drugev[,3]),]
vocev   <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(vocev, wt, na.rm=T)))
vocev   <- data.matrix(vocev[!is.nan(vocev[,3]),])
work    <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(work, wt, na.rm=T)))
work    <- data.matrix(work[!is.nan(work[,3]),])
edev    <- data.matrix(x %>% group_by(region, year) %>% summarize(weighted.mean(edev, wt, na.rm=T)))
edev    <- data.matrix(edev[!is.nan(edev[,3]),])

dimnames(drugev) <- dimnames(vocev) <- dimnames(work) <- dimnames(edev) <-
  list(NULL, c("region","year","xbar"))

par(mfrow=c(1,4))
par(fig=c(0,.29, 0,1))
plot(drugev[drugev[,"region"]==1,"year"],
     drugev[drugev[,"region"]==1,"xbar"]*100,
     type="b", pch=16, main="Drug Program",
     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
     axes=F, ylab="Percent", xlab="")
axis(1)
axis(2)
lines(drugev[drugev[,"region"]==2,"year"], drugev[drugev[,"region"]==2,"xbar"]*100,
      type="b", pch=17, col="dodgerblue")
lines(drugev[drugev[,"region"]==3,"year"], drugev[drugev[,"region"]==3,"xbar"]*100,
      type="b", pch=18, col="red")
lines(drugev[drugev[,"region"]==4,"year"], drugev[drugev[,"region"]==4,"xbar"]*100,
      type="b", pch=19, col="blue")
legend(1986, 80, c("Northeast","Midwest","South","West"),
       pch=16:19, col=c("skyblue2", "dodgerblue", "red","blue"),
       lty=1, bty="n", cex=1.1)
abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
par(new=T)
par(fig=c(.237,.527, 0,1))
plot(edev[edev[,"region"]==1,"year"],
     edev[edev[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Education",
     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
     axes=F, ylab="", xlab="")
axis(1)
lines(edev[edev[,"region"]==2,"year"], edev[edev[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
lines(edev[edev[,"region"]==3,"year"], edev[edev[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
lines(edev[edev[,"region"]==4,"year"], edev[edev[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
par(new=T)
par(fig=c(.473,.763, 0,1))
plot(vocev[vocev[,"region"]==1,"year"],
     vocev[vocev[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Job Training",
     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
     axes=F, ylab="", xlab="")
axis(1)
lines(vocev[vocev[,"region"]==2,"year"], vocev[vocev[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
lines(vocev[vocev[,"region"]==3,"year"], vocev[vocev[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
lines(vocev[vocev[,"region"]==4,"year"], vocev[vocev[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)
par(new=T)
par(fig=c(.71,1.0, 0,1))
plot(work[work[,"region"]==1,"year"],
     work[work[,"region"]==1,"xbar"]*100, type="b", pch=16, main="Work",
     xlim=c(1986, 2016), ylim=c(0,80), col="skyblue2",
     axes=F, ylab="", xlab="")
axis(1)
lines(work[work[,"region"]==2,"year"], work[work[,"region"]==2,"xbar"]*100, type="b", pch=17, col="dodgerblue")
lines(work[work[,"region"]==3,"year"], work[work[,"region"]==3,"xbar"]*100, type="b", pch=18, col="red")
lines(work[work[,"region"]==4,"year"], work[work[,"region"]==4,"xbar"]*100, type="b", pch=19, col="blue")
abline(v=seq(1985, 2015, 10), h=seq(0,80, 20), col="gray",lty=3)

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

Our results are summarized in @tbl-modelresults.

@@

## First discussion point {#sec-first-point}

@@

# Model details {#sec-model-details}

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(readr)
```

@@

The remainder of this paper is structured as follows.

# Data 
## Source

## Methodology
All data are not obtained directly through surveys/interviews, but are processed and calculated based on existing data.

 mass incarceration.xlsx

 incarceration 1925-2019

## Features
mass incarceration.xlsx

 incarceration 1925-2019
 year :1925-2019
 Prison :integer number
 Prison rate per(100k) easy to read and compare
 Jail
 Total
 Population
 Total Rate

 world incarceration rates
 rate
 rate18

 cumulative risk
 race :w(white) b(black)
 education
 cohort
 risk

Talk more about it.

```{r fig.height=8, fig.width=10 }
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

Talk way more about it. 
(@fig-bills2)

@@

@@

Our results are summarized in

@@

## First discussion point

@@

# Model details

@@

@@
